Fig1

### 2020-05-15 analysis/figure-1.Rmd
better suppl fig

sa <- png::readPNG("../figures/images/fig_supplfig1.png")
sa <- ggdraw() +  draw_image(sa, scale = 1)

@@

s1 <- plot_grid(s1a,s1b,s1c,s1d,s1e,s1f, ncol = 2, rel_heights = c(1,0.9,1.3))

supplfig1 <- plot_grid(sa, s1, ncol = 1, rel_heights = c(0.75,2))
supplfig1

>>>>

sa <- png::readPNG("../figures/images/fig_supplfig-1.png")
sa <- ggdraw() +  draw_image(sa, scale = 1)

@@

s1 <- plot_grid(s1a,s1b,s1c,s1d,s1e,s1f, ncol = 2, rel_heights = c(1,0.9,1.3),
                labels = c("B", "C"), label_size = 8)

supplfig1 <- plot_grid(sa, s1, ncol = 1, rel_heights = c(0.75,2), labels = c("A"), label_size = 8)
supplfig1
